Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
move text a bit

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way 
(other symbols).
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
\label{fig:alpha27}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified across all snapshots. 
Star symbols are color-coded by increasing SFR.
\label{fig:alpha16-28}}
\end{figure*}

@@

Similar MC properties in relation to those observed in the nearby Universe are found for \flower in its starburst phase (see bottom 
panel of \Fig{larsons_single} and \Fig{alpha27}).

@@

\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$\,200\,\kms (see \Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results are therefore robust.

\subsection{Origin of the MCs} \label{sec:origin}
The largest molecular structure identified is essentially the main disk of \flower which breaks down into smaller
substructures that are denser as we increase $n_{\rm cut}$. In any case,
the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

@@

Speculatively, the shallower slope found in the CMF for \flower compared to those observed in the nearby Universe (see \Sec{cmf}) may
suggest that the MCs of \flower are more massive compared to those observed in the nearby Universe.
% interpretation
Velocity dispersion and surface density are tightly connected to pressure. 
That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and 
since $P\propto\Sigma^2$).
In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of 
$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
from which massive star clusters or OB associations are to be formed.
% 
Therefore, speculatively... possible that ... the different CMF may suggest different IMF for \flower. 
This could be understood as different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  
% (While the first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
%As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
%metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.)

@@

We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy 
at the EoR using state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities
to identify MCs and their sub-structures in the main galaxy --- \flower\ --- of the
simulated 20\,Mpc h\pmOne box and in its satellites.
We decompose the molecular structures into non-overlapping tiles
by identifying a set of different density contours at different snapshots.
Using volumetric H$_2$ is essentially the same as identified molecular structures using
different contours in line emission (e.g., CO, CS, NH$_3$)
% and different molecular line tracers trace different MCs on different scales due to their
% different critical densities.
since the line luminosity scales with the molecular gas density (modulo optical depth effects).
% Our choice of density cut is analogues to the .... in \obs. It should be ... that both suffer from problem .... For instance, in \obs.. limited S/N.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local universe and at the peak epoch of cosmic \SF.
We also examine their properties at the different evolutionary stages of \flower and compare
them with observations.

@@

We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
Our results are thus robust/insensitive to the various density cuts of choice.
%However, our results are dependent on the numerical resolution of the simulation.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$.

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way 
(other symbols).
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
\label{fig:alpha27}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified across all snapshots. 
Star symbols are color-coded by increasing SFR.
\label{fig:alpha16-28}}
\end{figure}

@@

Similar MC properties in relation to those observed in the nearby Universe are found for \flower in its starburst phase (see bottom 
panel of \Fig{larsons_single} and \Fig{alpha27}).
% 
% \subsubsection{Temporal Evolution in Cloud Dynamics}
% What about all snapshots, where should the results for that go... \Fig{alpha16-28}, \Fig{larsons16-28}, \Fig{larsons16-28-highncut} and \Fig{alpha16-28-highncut}.

@@

\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$\,200\,\kms (see \Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results are therefore robust to the various density cuts of choice.

\subsection{Origin of the MCs} \label{sec:origin}
The largest molecular structure identified is essentially the main disk of \flower which breaks down into smaller
substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28} and \Fig{larsons16-28-highncut}). In any case,
the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

@@

% interpretation
Velocity dispersion and surface density are tightly connected to pressure. 
That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and 
since $P\propto\Sigma^2$).
In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of 
$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
from which massive star clusters or OB associations are to be formed.
% 
The shallower slope found in the CMF for \flower compared to those observed in the nearby Universe (see \Sec{cmf}) may
suggest that the MCs of \flower are more massive compared to those observed in the nearby Universe,
notwithstanding the limited numerical resolution of our simulation.
Together with the high $P_{\rm ext}$ may suggest different IMF for \flower compared to those observed in nearby galaxies.
This could be understood in the context of .... different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  
% (While the first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
%As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
%metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.)

@@

We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy 
at the EoR using state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities
to identify MCs and their sub-structures in the main galaxy --- \flower\ --- of the
simulated 20\,Mpc h\pmOne box and in its satellites.
We decompose the molecular structures into non-overlapping tiles
by identifying a set of different density contours at different snapshots.
Using volumetric H$_2$ is essentially similar to identifying molecular structures using
different contour levels on a surface brightness map of a molecular line tracer (e.g., CO, CS, NH$_3$),
since the line luminosity scales with the molecular gas density (modulo optical depth effects).
% Our choice of density cut is analogues to the .... in \obs. It should be ... that both suffer from problem .... For instance, in \obs.. limited S/N.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
We also examine their properties at the different evolutionary stages of \flower and compare
them with observations.

@@

We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
Our results are thus insensitive to the various density cuts of choice.
%However, our results are dependent on the numerical resolution of the simulation.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures.
Such a high velocity dispersion likely results from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as 
result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$.
